---
title: "AppEx 16: Inference for Regression"
author: ""
date: ""
output: 
  html_document:
    toc: false
    number_sections: false
    df_print: paged
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```


## Packages and Data

```{r packages}
library(tidyverse)
library(infer)
library(broom)
library(mosaicData)
```

The Pioneer Valley Planning Commission collected data in Florence, MA for 90 
days from April 5 to November 15, 2005 using a laser sensor, with breaks in the 
laser beam recording when a rail-trail user passed the data collection station.

```{r load_data}
data(RailTrail)
```

## Exercises

### Exercise 1

Consider a regression model with a response as `volume` and a single predictor
of `avgtemp`. Create a 95% confidence interval for the population slope using
a simulation-based inference approach and a CLT-based inference approach. Do
your results agree and is the coefficient significantly different from 0?

### Exercise 2

Consider the population model

$$\mbox{volume} = \beta_0 + \beta_1 \mbox{weekday} + \beta_2 \mbox{avgtemp} +
\beta_3 \mbox{precip} + \epsilon$$

Compute a 95% confidence interval for each population coefficient.

### Exercise 3

Using your fitted model from Exercise 2, check if the four linear model
conditions are satisfied. If they are not, how does this impact your
confidence intervals in Exercise 2?

### Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.
